A Gentle Introduction into Structural Causal Models

### 2021-05-15 draft.Rmd
xyt
mathpazo font

---
title: "A Gentle Introduction into Structural Causal Models"
author: 
- Daniel Saggau $\boldsymbol{\cdot}$ `daniel.saggau@campus.lmu.de`
- Department of Statistics, Ludwig Maximilian University Munich, Germany
date: " April 5th, 2021"
output: 
  pdf_document:
        number_sections: yes
        fig_caption: yes
link-citations: yes
linkcolor: blue
fontsize: 12
linestretch: 1.5
citation_package: --biblatex
bibliography: [ref.bib]
nocite: '@*'

---

@@

Another issue in this paper is understanding the relationship of time and causality.
SCMs make the assumption that causal relationships hold over time[@peters_elements_2017].
These vague definitions of time is more prevalent in social sciences. 
Meanwhile hard sciences deal with time in a more concise manner. 
Differential equations model time on a more mechanic manner (@mooij2013ordinary).

>>>>

---
title: "A Gentle Introduction into Structural Causal Models"
author: 
- Daniel Saggau $\boldsymbol{\cdot}$ `daniel.saggau@campus.lmu.de`
- Department of Statistics, Ludwig Maximilian University Munich, Germany
date: " April 5th, 2021"
output: 
  pdf_document:
        number_sections: yes
        fig_caption: yes
link-citations: yes
linkcolor: blue
fontsize: 12
fontfamily: mathpazo 
linestretch: 1.5
citation_package: --biblatex
bibliography: [ref.bib]
nocite: '@*'
---

@@

Another issue in this paper is understanding the relationship of time and causality.
SCMs make the assumption that causal relationships hold over time[@peters_elements_2017].
These vague definitions of time is more prevalent in social sciences. 
Meanwhile hard sciences deal with time in a more concise manner. 
Differential equations model time on a more mechanic manner [@mooij2013ordinary].
